---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QSPtools

<!-- badges: start -->
<!-- badges: end -->

The goal of QSPtools is to put the various functions developed by the Quantative Sciences Program into one place.  There are functions that:

* set the netowrk path to the Brown network
* directly read data from select studies that are saved on the Brown network
* perform data checking


## Installation

You can install the  development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dougtommet/QSPtools")
```
## Example


```{r example}
library(QSPtools)

# Network functions
my_project <- fs::path(QSPtools::network_path(), "Projects", "My_Project")
my_project
# df <- readr::read_csv(fs::path(my_project, "my_data.csv"))

# Read data functions
# QSPtools::sages_data("si", frozen = TRUE, frozen_date = "2021-05-03")
# QSPtools::sagesII_data("si", frozen = TRUE, frozen_date = "2022-10-05")

# Check data functions
df <- tibble::tibble(a = c(rep(1, 10), rep(2, 10)),
                     b = c(rep(1, 5), rep(2, 10), rep(3, 5)))
df <- df %>%
  dplyr::mutate(new_var = a + b)
df %>%
  QSPtools::checkvar(new_var, a, b)
```
